Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-04 doc/main_jfm.tex
updates

The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,

\begin{equation}
\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit.eps}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and we set the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT $\approx35$ pN nm.

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0$ and the dimensionless shear rate 
is referred from~\cite{Finken08}
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu=1$ cP the fluid viscosity is used through this work.

>>>>

The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,

\begin{equation}
\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
  \caption{Comparison of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm from ~\cite{Ryham16}. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT $\approx35$ pN nm.

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate 
is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity is used through this work.
